---
title: "`r params$title`"
author: "`r params$author`"
date: "`r Sys.Date()`"
output: pdf_document
params:
  df: NULL
  author: "Expert"
  title: "Data Report"
---

```{r setup, include=FALSE}
knitr::opts_chunk_set(echo = FALSE, message = FALSE, warning = FALSE)
library(ggplot2)
library(knitr)
library(dplyr)
```

# Executive Summary

This report provides an automated analytical overview of the uploaded dataset.

## Dataset Metadata
- **Total Rows:** `r nrow(params$df)`
- **Total Columns:** `r ncol(params$df)`

# Statistical Profiling

## Missing Value Summary
```{r missing}
m <- colSums(is.na(params$df))
m_df <- data.frame(Variable = names(m), MissingCount = m)
kable(m_df)
```

## Numeric Descriptive Statistics
```{r stats}
num_df <- params$df[, sapply(params$df, is.numeric), drop = FALSE]
if(ncol(num_df) > 0) {
  sum_df <- do.call(rbind, lapply(num_df, function(x) {
    data.frame(
      Min = min(x, na.rm = TRUE),
      Mean = mean(x, na.rm = TRUE),
      Max = max(x, na.rm = TRUE)
    )
  }))
  kable(sum_df)
}
```

# Graphical Analysis

## Primary Distributions
```{r plots, fig.height=4}
if(ncol(num_df) > 0) {
  first_num <- names(num_df)[1]
  ggplot(params$df, aes_string(x = first_num)) +
    geom_histogram(fill = "steelblue") +
    theme_minimal() + labs(title = paste("Distribution of", first_num))
}
```

# Conclusion
The dataset has been successfully profiled. Further analysis can be conducted based on the identified distributions and statistics.

---
*Report Generated by Automatic CSV Data Analysis & Report Generator*
